---
title: "Mock Practice Report"
author: "Caroline Thomas"
date: "4/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE, warning=FALSE,message=FALSE}
library(tidyverse)
library(ggplot2)
library(formattable)
```

```{r, echo=FALSE}
data <- read.csv("practicedata.csv") %>%
  mutate(.,
         player = X..i..,
         strikes = X..i...1,
         balls = X..i...2,
         in_out = X..i...3,
         up_down = X..i...4,
         change1 = X..i...5,
         win_loss = X..i...6,
         change2 = X..i...7,
         xloc = X..i...8,
         yloc = X..i...9) %>%
  select(., player, strikes, balls, in_out, up_down, change1, win_loss, change2, xloc, yloc)
```

## Team Summary

### Pitches seen:
```{r, echo=FALSE}
pitches_team <- count(data)
```
**During this practice, the team saw `r pitches_team$n` pitches.**

### Team Win and Loss Percentages:
```{r, echo=FALSE}
#win/loss perc
win_loss_perc <- data %>%
  group_by(win_loss) %>%
  count() %>%
  mutate(., percentage = n/pitches_team$n *100)

formattable(win_loss_perc, align = "l", list(area(col = 3) ~ function(x) percent(x/100, digits = 1)))

pie(win_loss_perc$percentage, labels = round(win_loss_perc$percentage,2), col = c("lightcoral", "lightgreen"),
    main = "Percentage of Wins and Losses for Team")
legend("bottomright", legend = win_loss_perc$win_loss , fill = c("lightcoral", "lightgreen"))
```

### Team Situational Report

#### Number of pitches seen in each situation:
```{r, echo=FALSE}
pitches_sit <- data %>%
  group_by(strikes, balls) %>%
  count()

formattable(pitches_sit, align = "l")
```

#### Win percentage for each count:
```{r, echo=FALSE, message=FALSE}
win_loss_sit <- data %>%
  group_by(strikes, balls, win_loss)%>%
  count() %>%
  mutate(
    pitches = n
  ) %>%
  select(., -n)

win_loss_sit <- left_join(win_loss_sit, pitches_sit) %>%
  mutate(., pitches_seen = n) %>%
  select(., -n) %>%
  mutate(., Percentage = round(pitches/pitches_seen*100,2)) %>%
  filter(., win_loss == "Win")

```

```{r, echo=FALSE}
color_tile_mean <- function (...) {
  formatter("span", style = function(x) {
    style(display = "block",
          padding = "0 4px", 
          `border-radius` = "4px", 
          `background-color` = ifelse(x < 50 , "lightcoral", ifelse(x > 60, "lightgreen", "khaki"))) # Remember to change the colors!
  })}

formattable(win_loss_sit, align = "l", list(`Percentage` = color_tile_mean()))
```


## Player Summaries

```{r, echo=FALSE}
pitches_player <- data %>%
  group_by(player) %>%
  count()
```

### Win percentage for each player:
```{r, echo=FALSE, message=FALSE}
win_loss_player <- data %>%
  group_by(player, win_loss)%>%
  count() %>%
  mutate(
    pitches = n
  ) %>%
  select(., -n)

win_loss_player <- left_join(win_loss_player, pitches_player) %>%
  mutate(., pitches_seen = n) %>%
  select(., -n) %>%
  mutate(., Percentage = round(pitches/pitches_seen*100,2))

```

```{r, echo=FALSE}

pitch_counts <- win_loss_player %>%
  mutate(Player = paste0(player,"\n", "# of Pitches Seen: ",pitches_seen))

#formattable(pitches_player, align = "l")

#bar chart win/loss percentage

ggplot(pitch_counts, aes(fill = win_loss, y = Percentage, x = Player)) +
  geom_bar(position = "fill", stat = "identity") +
  scale_fill_manual(values = c("lightcoral","lightgreen"), "Win/Loss") +
  ggtitle("Proportion of Wins/Loss for Each Player") +
  theme_classic() +
  xlab("Player") +
  ylab("Proportion of Wins and Losses") 

```


### Player Situational Reports
**Charts display the strikezone, the player's most frequent "hot zone", pitches that were seen, and whether pitches were a win or loss.**

```{r, echo=FALSE}
pitches_sit_play <- data %>%
  group_by(player, strikes, balls) %>%
  count()
```

```{r, echo=FALSE, message=FALSE}
win_loss_sit_play <- data %>%
  group_by(player, strikes, balls, win_loss)%>%
  count() %>%
  mutate(
    pitches = n
  ) %>%
  select(., -n)

win_loss_sit_play <- left_join(win_loss_sit_play, pitches_sit_play) %>%
  mutate(., pitches_seen = n) %>%
  select(., -n) %>%
  mutate(., Percentage = round(pitches/pitches_seen*100,2)) %>%
  filter(., win_loss == "Win")

```


### Jordan Acosta, #23:

```{r, echo=FALSE}
color_tile_mean <- function (...) {
  formatter("span", style = function(x) {
    style(display = "block",
          padding = "0 4px", 
          `border-radius` = "4px", 
          `background-color` = ifelse(x < 50 , "lightcoral", ifelse(x > 60, "lightgreen", "khaki"))) # Remember to change the colors!
  })}

formattable(win_loss_sit_play[1,], align = "l", list(`Percentage` = color_tile_mean() ))
```


```{r, echo=FALSE}
#For Jordan Acosta
data1 <- data %>%
  filter(player == "Acosta, Jordan #23")

plot(1, type = "l", main = "Jordan Acosta", xlab = "", ylab = "", xlim = c(0,5), ylim = c(0,5), yaxt = 'n', xaxt = 'n', pch = 16)
polygon(x = c(1,4,4,1), y = c(1,1,4,4), col = adjustcolor("lightcoral",alpha.f=0.5))
polygon(x = c(1,3,3,1), y = c(2,2,4,4), col = adjustcolor("lightgreen", alpha.f = 0.5))
points(x = data1$xloc, y = data1$yloc, pch = 16, col = data1$win_loss)
legend("bottomright", legend = c("Win", "Loss"), col = c("red", "black"), pch = 16, box.lty = 0)
legend("bottom", legend = c("Strikezone", "Hot Zone"), col = c("lightcoral", "lightgreen"), pch = 15, box.lty = 0)
grid(nx = 5, ny = 5, col = "black")
```

### Peyton Allen, #3

```{r, echo=FALSE}
color_tile_mean <- function (...) {
  formatter("span", style = function(x) {
    style(display = "block",
          padding = "0 4px", 
          `border-radius` = "4px", 
          `background-color` = ifelse(x < 50 , "lightcoral", ifelse(x > 60, "lightgreen", "khaki"))) # Remember to change the colors!
  })}

formattable(win_loss_sit_play[2:3,], align = "l", list(`Percentage` = color_tile_mean() ))
```

```{r, echo=FALSE}
#For Peyton Allen
data2 <- data %>%
  filter(player == "Allen, Peyton #3")

plot(1, type = "l", main = "Peyton Allen", xlab = "", ylab = "", xlim = c(0,5), ylim = c(0,5), yaxt = 'n', xaxt = 'n', pch = 16)
polygon(x = c(1,4,4,1), y = c(1,1,4,4), col = adjustcolor("lightcoral",alpha.f=0.5))
polygon(x = c(2,4,4,2), y = c(2,2,4,4), col = adjustcolor("lightgreen", alpha.f = 0.5))
points(x = data2$xloc, y = data2$yloc, pch = 16, col = data2$win_loss)
legend("bottomright", legend = c("Win", "Loss"), col = c("red", "black"), pch = 16, box.lty = 0)
legend("bottom", legend = c("Strikezone", "Hot Zone"), col = c("lightcoral", "lightgreen"), pch = 15, box.lty = 0)
grid(nx = 5, ny = 5, col = "black")
```
